---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%", 
  eval = FALSE
)
```

# callthat

<!-- badges: start -->
[![R-CMD-check](https://github.com/edgararuiz/callthat/workflows/R-CMD-check/badge.svg)](https://github.com/edgararuiz/callthat/actions)
[![Codecov test coverage](https://codecov.io/gh/edgararuiz/callthat/branch/master/graph/badge.svg)](https://codecov.io/gh/edgararuiz/callthat?branch=master)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/callthat)](https://CRAN.R-project.org/package=callthat)
<!-- badges: end -->

`callthat` is meant for `plumber` API developers who plan to distribute their APIs inside an R package.  This package enables the testing of the API's endpoints within the `testthat` framework.  This allows the R Checks to also confirm that the endpoints still behave as expected.  

The ultimate goal of `callthat` is to ensure that the package's automated testing catches issues with the API even if the developer did not perform unit testing. 

## Installation

The development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("edgararuiz/callthat")
```

## Usage

### `plumber` API in your package

Place your API in the `inst/plumber` folder of your package.  That way  `plumber::available_apis("MyPakcageName")` can locate the APIs, after your package is installed.

In `MyPakcageName/inst/plumber/sample-api`:

```{r, eval = FALSE}
library(plumber)

#* Runs a prediction of the Weight
#* @get /predict
function(weight) {
  wtg <- as.numeric(weight)
  model <- stats::lm(mpg ~ wt, data = datasets::mtcars)
  stats::predict(model, newdata = data.frame(wt = wtg))
}
```

### Inside the `testthat` folder

```{r, eval = TRUE}
library(testthat)
library(callthat)
library(httr)
```

Create the test using the same name as the name of the API.  Add the prefix `test-plumber`.  

In `MyPakcageName/tests/testthat/test-plumber-sample-api.R`:

```{r, eval = FALSE}
test_that("Show how to use test", {
  expect_silent({
    
    # ------------- Start plumber API ------------------- 
    local_api <- call_that_plumber_start(
      system.file("plumber/sample-api", package = "MyPackageName")
      )
    
    # ------------- Start test session ------------------ 
    api_session <- call_that_session_start(local_api)
  })
  expect_s3_class(
    
    # ---------------- Make API call --------------------
    get_predict <- call_that_api_get(
      api_session, 
      endpoint = "predict", 
      query = list(weight = 1)
      ),
    "response"
  )
  
  # ---------- Run tests against response ---------------
  ## Test to confirm that the response was a success
  expect_equal(
    get_predict$status_code,
    200
  )
  ## Test to confirm the output of the API is correct
  expect_equal(
    round(content(get_predict)[[1]]),
    32
  )
  
  # ----- Close the session, and the plumber API --------
  expect_null(
    call_that_session_stop(api_session)
  )
})
```

### Managing the API tests

`callthat` matches the API to the test by name.  The `call_that_available_tests()` returns a table with the available APIs in your package, and it displays if there is a matching test.

```{r, eval = FALSE}
call_that_available_tests()
```

```{r, echo = FALSE, eval = TRUE}
call_that_available_tests(
  plumber_directory = "inst/plumber",
  test_directory = "inst/tests"
)
```

### Run tests against the published API

`callthat` makes it possible to run the exact same tests used for unit testing, for integration testing.  

Open a connection with the published API.  If that API is running in RStudio Connect, then use `call_that_rsc_connection()`, otherwise use the generic `call_that_connection()`.

```{r, eval = TRUE}
published_api <- call_that_rsc_connection(
  url = "https://colorado.rstudio.com/rsc/callthat/testapi",
  key = Sys.getenv("RSC_TOKEN") # Optional, only if access to your API is restricted
  )

published_api
```

The `call_that_test_remote()` functions runs the tests for the API, but it is possible to also pass the published API's connection so that the tests run remotely.

```{r}
call_that_test_remote("sample-api", published_api)
```

```{r, echo = FALSE, eval = TRUE}
call_that_test_remote("sample-api", published_api, test_directory = "inst/tests")
```

